\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-04 casestudies.tex
edit on QIIT para

Our implementation of family polymorphism retains the computation
ability of the host proof assistant;
Gallina code generated for \lsti{ImpTI} and \lsti{ImpCP} are directly
runnable in Coq.
The two abstract interpreters can be extracted into OCaml;
we put them to test over simple queries.

>>>>

Our implementation of family polymorphism retains the computation
ability of the host proof assistant;
the two abstract interpreters in \lsti{ImpTI} and \lsti{ImpCP} are
directly runnable in Coq.
We also extract them to OCaml and put them to test over simple queries.

### 2022-11-04 metatheory-condensed.tex
edit on QIIT para

The definitive version is formalized in a logical framework with
quotient inductive-inductive types~\cite{nordvall2010inductive,altkap2016},
available as a supplemental file in Agda syntax.
%
We also typeset a more complete set of rules than
the space allows and present it in a supplemental appendix.
%
Another supplemental appendix gives a larger-scale example than
\cref{fig:stlc-linkage-typing} showing how families are modeled and
type-checked using linkages and linkage transformers.

>>>>

The definitive version containing all the rules in \TT is stated in
terms of a meta\-language supporting quotient inductive-inductive types
(QIITs)~\cite{nordvall2010inductive,altkap2016}.
QIITs support equality constructors, which facilitate the expression of
conversion rules (e.g., \ruleref{tmeq/sub/id}).
The formalization is available as a supplemental file in Agda syntax,
though it is not checked by Agda because Agda does not support QIITs
natively.
An effort to mechanize the formalization is ongoing, using Agda's
\lsti{REWRITE} pragma to replace the limited uses of equality reflection.
%a \textbf{pen-and-paper} formalization
%assuming the facility of quotient inductive-inductive
%types~\cite{nordvall2010inductive,altkap2016} and extensional equality
%(equality reflection), available as a supplemental file in a
%\textbf{(pseudo-)Agda syntax}. Our formalization is directly following
%Agda syntax and type-checking (equality-checking) is done manually,
%leaving traces in the comments. We are currently working on mechanizing
%it and relying on Agda's rewriting mechanism to replace our limited
%usage of equality reflection.

We also typeset a more complete set of rules than the space allows and
present it in a supplemental appendix.
%
Another supplemental appendix gives a more complete example than
\cref{fig:stlc-linkage-typing} showing how families are modeled and
type-checked using linkages and linkage transformers.
